# 3. Sports Cards

In this experiment, the experimenters invited consumers at a sports card trading show to bid against one other bidder for a pair trading cards.  We abstract from the multi-unit-auction details here, and simply state that the treatment auction format was theoretically predicted to produce lower bids than the control auction format.  We provide you a relevant subset of data from the experiment.

In this question, we are asking you to produce p-values and confidence intervals in three different ways: 

1. Using a `t.test`; 
2. Using a regression; and,
3. Using randomization inference. 

```{r load cards data }
d <- fread('../data/list_data_2019.csv')
```

1. Using a `t.test`, compute a 95% confidence interval for the difference between the treatment mean and the control mean. After you conduct your test, write a narrative statement, using inline code evaluation that describes what your tests find, and how you interpret these results. (You should be able to look into `str(t_test_cards)` to find the pieces that you want to pull to include in your written results.) 

```{r cards t-test}


t_test_cards <- t.test(d[uniform_price_auction==1,bid],d[uniform_price_auction==0,bid]) # this should be the t.test object. Extract pieces from this object in-text below the code chunk. 
str(t_test_cards.p.value)

```

**Our confidence interval is `r (t_test_cards$conf.int[1]` and `r (t_test_cards$conf.int[2]`**

2. In plain language, what does this confidence interval mean? 

**We are 95% sure that that the difference for the means between the treatment and control groups is between [-3.56, -20.85]. The mean difference between treatment and control is negativeso it seems that the treatment has negative effect on bid value.**

3. Conduct a randomization inference process using an estimator that you write by hand (i.e. in the same way as earlier questions). On the sharp-null distribution that this process creates, compute the 2.5% quantile and the 97.5% quantile using the function `quantile` with the appropriate vector passed to the `probs` argument. After you conduct your test, write a narrative statement of your test results. 

```{r cards randomization inference} 
## first, do you work for the randomization inference

randomize_function <- function( ){
  return(sample(d[,uniform_price_auction]))
}

ri_function <- function( ) {
  po_control <- d[,bid]
  po_treatment <- po_control # we want to test under the sharp null
  treatment <- randomize_function()
  outcomes <- po_treatment * treatment + po_control * (1 - treatment)
  ri_ate <- mean(outcomes[treatment==1]) - mean(outcomes[treatment==0])
  return(ri_ate)
}

# Run 10000 trials on the distribution 
ri_distribution_price <- replicate(10000, ri_function()) # numeric vector of length equal to your number of RI permutations

ri_quantiles    <- quantile(ri_distribution_price, probs=c(0.025, 0.975)) # there's a built-in to pull these.
print(ri_quantiles)
```

** Using Random Inference we can calculate a 95% confidence interval from our random sampling by finding the 2.5% and 97.5% values and comparing those to the mean. The range of all the treatment effects does mirror the range of our confidence interval. If we ran the test many more times we'd probably get closer to a range of 17.24.** 

4. Do you learn anything different if you regress the outcome on a binary treatment variable? To answer this question, regress `bid` on a binary variable equal to 0 for the control auction and 1 for the treatment auction and then calculate the 95% confidence interval using *classical standard errors* (in a moment you will calculate with *robust standard errors*). There are two ways to do this -- you can code them by hand; or use a built-in, `confint`. After you conduct your test, write a narrative statement of your test results. 

```{r cards ols regression}
mod <- lm(bid ~ uniform_price_auction,data=d) # this should be a model object, class = 'lm'. 
summary(mod)

confint(mod,"uniform_price_auction")
```


**Ans: We see that the coefficient for the uniform_price_auction is -12.206 with std Error of 4.327 . This is quite similar to difference in means we get from t.test **  

5. Calculate the 95% confidence interval using robust standard errors, using the `sandwich` package. There is a function in `lmtest` called `coefci` that can help with this. It is also possible to do this work by hand. After you conduct your test, write a narrative statement of your test results.

```{r cards robust ci}
coefci(mod)
```

  
**Ans: We see from the regression test that the 95% confidence interval is about the same reported by the the t.test **   

6. Characterize what you learn from each of these different methods -- are the results contingent on the method of analysis that you choose? 

**They don't seem to be, unless I've made an error. The robust standard errors and the classical standard errors mirror one another, as do the values from the t-test. The values from the RI that we generated also showed a similar range of possible outcomes, though I was confused at first by how to think about them.**
